Explore anomalies

### 2017-11-20 analysis/evi/explore_anomalies.Rmd
update explore anomalies evi. adding png

pdf(file=paste0(di, "/out/anomalies/evi/plot_anoma_EVI_clu_a.pdf"), height = 7, width = 7)
plot_a_clu
dev.off()
```

@@

pdf(file=paste0(di, "/out/anomalies/evi/plot_anoma_EVI_clu_nora.pdf"), height = 7, width = 7)
plot_nora_clu 
dev.off()
```

@@

pdf(file=paste0(di, "/out/anomalies/evi/plot_anoma_EVI_clu_sa.pdf"), height = 7, width = 7)
plot_sa_clu
dev.off()
```

@@

pdf(file=paste0(di, "/out/anomalies/plot_anoma_EVI_pop_a.pdf"), height = 14, width = 14)
plot_a_pop
dev.off()
```

@@

pdf(file=paste0(di, "/out/anomalies/plot_anoma_EVI_pop_nora.pdf"), height = 14, width = 14)
plot_nora_pop 
dev.off()
```

@@

pdf(file=paste0(di, "/out/anomalies/plot_anoma_EVI_pop_sa.pdf"), height = 14, width = 14)
plot_sa_pop
dev.off()
```

>>>>

plot_a_clu
pdf(file=paste0(di, "/out/anomalies/evi/plot_anoma_EVI_clu_a.pdf"), height = 7, width = 7)
plot_a_clu
dev.off()
```

@@

plot_nora_clu 
pdf(file=paste0(di, "/out/anomalies/evi/plot_anoma_EVI_clu_nora.pdf"), height = 7, width = 7)
plot_nora_clu 
dev.off()
```

@@

plot_sa_clu
pdf(file=paste0(di, "/out/anomalies/evi/plot_anoma_EVI_clu_sa.pdf"), height = 7, width = 7)
plot_sa_clu
dev.off()
```

@@

plot_a_pop
pdf(file=paste0(di, "/out/anomalies/plot_anoma_EVI_pop_a.pdf"), height = 14, width = 14)
plot_a_pop
dev.off()
```

@@

plot_nora_pop 
pdf(file=paste0(di, "/out/anomalies/plot_anoma_EVI_pop_nora.pdf"), height = 14, width = 14)
plot_nora_pop 
dev.off()
```

@@

plot_sa_pop
pdf(file=paste0(di, "/out/anomalies/plot_anoma_EVI_pop_sa.pdf"), height = 14, width = 14)
plot_sa_pop
dev.off()
```
